Digital History in Finland, 1488-1828

### 2016-11-17 inst/examples/20161117-manuscript.Rmd
ok

```{r init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.path = "figure-2016-manuscript/")
# Set locale
tmp <- Sys.setlocale(locale="UTF-8")

@@

```{r title_length, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
df <- dfo %>% group_by(publication_year) %>%
              summarize(median_title_length = median(title_wordcount),
	      		mean_title_length = mean(title_wordcount),
	      		n = n())

@@

```{r title_length_by_gatherings, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
top.gatherings <- setdiff(names(top(dfo, "gatherings", 5)), "NA")

>>>>

```{r init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.path = "figure-2016-manuscript/", dev="CairoPNG")
# Set locale
tmp <- Sys.setlocale(locale="UTF-8")

@@

```{r title_length, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
df <- dfo %>% group_by(publication_year) %>%
              summarize(median_title_length = median(title_wordcount),
	      		mean_title_length = mean(title_wordcount),
	      		n = n())

@@

```{r title_length_by_gatherings, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=15}
top.gatherings <- setdiff(names(top(dfo, "gatherings", 5)), "NA")
